---
title: "Why is chicken so popular as poultry products compare to rest."
output:
  word_document: default
  pdf_document:
    df_print: pander
---
** STEP 1: ** 
We will extract data from source ["http://www.nationalchickencouncil.org/about-the-industry/statistics/per-capita-consumption-of-poultry-and-livestock-1965-to-estimated-2018-in-pounds/"]

** Title should be : Per Capita Consumption of Poultry and Livestock, 1965 to Estimated 2018, in Pounds. ** 

You can see table data upto 2018 and forcasted for 2019.
Note: All poultry and livestock products are on a retail weight basis, except “other chicken” and “turkey” which are reported by USDA on a carcass-weight basis.
Fish/shellfish is reported by The National Marine Fisheries Service on an edible weight basis.

** NOTE **
* A broiler (Gallus gallus domesticus) is any chicken that is bred and raised specifically for meat production *
I just run chicken and broilers,although they are same but want to show the market consumption for meat products go hand in hand and I am not setting up any biases.

# Import libraries for rendering to pdf or html output
```{r}
library("knitr")
library("rmarkdown")
library("markdown")
```
# setiing up parameters
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(progress = FALSE, verbose = FALSE)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```
# Lets import necessary packages 
```{r}
library(rvest) # Good for webscrapping
library(tidyverse) # We can use package like dplyr, ggplot 
```
# Data source

We will read the data from the websource itself.

Need to address the Question before we dive in data??
Americans buy more chicken than any other food at the center of the plate. Chicken consumption per capita has increased nearly every year since the mid 1960’s, while red meat consumption has steadily declined.

We will gather data to show these output.

** Whenever you are trying to show visually any Time Series graph use Line plot to convey. Line plots are always good visuallization for Time Series Data like this. **
# Per capita consumption
```{r}
url <- "https://www.nationalchickencouncil.org/about-the-industry/statistics/per-capita-consumption-of-poultry-and-livestock-1965-to-estimated-2012-in-pounds/"

```
# Lets read the dataframe with the help of read_html
```{r}
poultry_list <- read_html(url) %>%  # Read the data from url and convert it into html_table
  html_table()
```
# Lets convert into dataframe 
```{r}
poultry_df <- data.frame(poultry_list[[1]]) # We will convert first list into dataframe.
head(poultry_df) # Lets look at first six rows
```
# Look at the tail of dataframe: Good Practice 
```{r}
tail(poultry_df) # See the last two rows in Year column it says estimate 2018 and forcast 2019 as Date column so we need to fix that before we convert whole column into date object
```
# Fixing Year column
* Lets remove the word estimate and forecast for now. We just want year to be numeric rather than character
```{r}
poultry_df$Year <- gsub("[^0-9]","",poultry_df$Year) # gsub substitutes before with after.
tail(poultry_df)
```
# Lets look at range and class column
```{r}
range(poultry_df$Year) # Lets look the range of year, We are close to end of 2018 as of today.
class(poultry_df$Year) # Also notice that R doesnt render date when importing so its always better to check before you do any analysis.
```
# Lets fix year column 
* As it says character we need to convert it into numeric
```{r}
poultry_df$Year <- as.numeric(poultry_df$Year)
class(poultry_df$Year)
range(poultry_df$Year)
```
# lets visualize our dataset with skimr package
```{r}
library(skimr) # ver good summarised way of looking dataframe.
skim(poultry_df)
```
# Lets clean up the column name
* There is one more column called other.chicken. I guess its just different type. You can merge these two table and make one whole chicken but for now we will leave it like that without creating biases. So we will leave other chicken and total chicken for now.
```{r}
poultry_df <- poultry_df %>% 
              rename(Seafood = Commercial.Fish...Shell.Fish,  # We will just call it seafood
                     Chicken = Total.Chicken)
colnames(poultry_df)
```
# Normalization before comparison
We need to calculate the percentage change from the baseline. otherwise our plot will start from different bases. So lets normalise the data.
look into first line of the year 1960.
Beef,   Pork,   Chicken, Broilers,  Turkey,  Seafood
```{r}
head(poultry_df,1)
```
# Normalization
```{r}
poultry_df <- poultry_df %>% 
  select(Year, Beef, Pork, Broilers, Chicken, Turkey, Seafood ) %>%  # We will focus on 5 main categories.
  mutate(percent_change_Beef= (Beef- 63.3)/63.3*100 , 
        percent_change_Pork = (Pork - 59.1)/59.1 *100,
        percent_change_Broilers = (Broilers - 23.6)/23.6 * 100,
        percent_change_Chicken = (Chicken - 28)/28 *100,
        percent_change_Turkey = (Turkey - 6.2)/6.2 *100,
        percent_change_Seafood = (Seafood - 10.3)/10.3 *100)
       # value of particular year - base value then divide by base value * 100 % 
head(poultry_df, 3)
# Look at first line will be all zero as baseline and look at second line it shows the change from last year.
```
# Lets look at colnames
```{r}
colnames(poultry_df)
```
# Lets confirm unique type of meat so that we can get gist of it.
** Sanity check ** 
```{r, echo=FALSE}
#unique(percent_poultry_df$type_of_meat)
```
# creating a subset for just raw sales for graphing
```{r}
colnames(poultry_df)
raw_sales <- poultry_df %>% 
              select(-c(8:13)) %>% 
  gather("type_of_meat", "poultry_df", 2:7) # will create two new columns type_of_meat & poultry_df and gather them
tail(raw_sales)
unique(raw_sales$type_of_meat)
```
# Finding Intersection and rendering after initial plot
I have created this plot after finding out the intersection on rough draft as you will see below in ggplot that there is intersection of chicken with pork and with beef in year 1982 and 1992
```{r}
raw_sales_pork <- raw_sales %>% filter(Year >= "1982" & type_of_meat == "Pork")
raw_sales_beef <- raw_sales %>% filter(Year >= "1992" & type_of_meat == "Beef")
raw_sales_chicken <- raw_sales %>% filter(Year >= "1982" & type_of_meat == "Chicken")
```
# Plot
```{r}
g_sales <- ggplot()+
  geom_line(data = raw_sales, aes ( x= Year, y = poultry_df, group = factor(type_of_meat), color = factor(type_of_meat)), size = 2, alpha = 1.0)+ # First 5 Main line in plot.
  
#Raw_sales_beef
geom_line(data = raw_sales_beef, aes(x = Year, y = poultry_df, group = 1), color = "grey", size = 1, alhpa = 0.7)+ # Adding another grey line on top of previous line kind of geom_smooth on raw_sales_beef
  
# Raw_sales_chicken
geom_line(data = raw_sales_chicken, aes(x = Year, y = poultry_df, group = 1), color = "green4", size = 1, alpha = 0.7)+

#Raw_sales_broilers : We can basically ignore broilers intersection with beef, pork as broilers and chicken are parallel to one another.
  
#Raw_sales_pork
geom_line(data = raw_sales_pork, aes(x = Year, y = poultry_df, group = 1 ), color = "grey", size = 1, alpha = 0.7)+ # Adding another grey line on top of previous line kind of geom_smooth on raw_sales_pork
  
# Raw_sales_Turkey & Raw_sales_seafood data we can look into seperate graph as it will be worthless to compare against chicken, beef or pork.

# Adding geom_point (Intersection dot )
geom_point(aes(x= 1973, y = 81), size = 4, color = 'red')+ # The value x= 1973 and y= 81 is from looking at graph and adding big red dot(POINT)
geom_point(aes (x= 1992, y = 66), size = 4, color = 'green4')+ # Intersection of chicken and beef
geom_point(aes (x = 1982,  y= 47), size = 4, color = 'green')+


# Lets add some text in graph
geom_text(aes (x = 1965, y = 100), label = "Beef_Shortage: 1973", hjust = 0, color = 'red', fontface = "bold")+
geom_text(aes (x = 1965, y = 110), label = "Crop crisis directly impact beef supply", hjust = 0, color = 'red')+
geom_text(aes (x = 1984, y = 28), label = "Chicken surpasses Pork: 1982", fontface = "bold")+
geom_text(aes(x = 2000, y =42), label = "Pork remain stable", color = 'blue3')+
geom_text(aes(x= 2000, y = 95), label = "Chicken outpace beef : 1992", fontface = "bold", size =4)+
geom_text(aes(x = 2003, y = 8), label = "Seafood and Turkey have gain slight market", fontface = "bold", size = 4)+

# Lets label Chicken, pork ,beef, Turkey, broilers and Beef POSITION
# Usually we all read left to right so if you are setting up trend line label prefarably on left.
geom_text(aes(x= 1962,  y = 78), label = "Beef", color = 'red3', fontface = "bold", size = 4)+
geom_text(aes(x= 1962,  y = 20), label = "Chicken", color = 'green3', fontface = "bold", size = 4)+
geom_text(aes(x= 1962,  y = 42), label = "Broilers", color = 'yellow3', fontface = "bold", size = 4)+
geom_text(aes(x= 1962,  y = 50), label = "Pork", color = 'blue3', fontface = "bold", size = 4)+
geom_text(aes(x= 1962,  y = 14), label = "Turkey", color = 'pink3', fontface = "bold", size = 4)+
geom_text(aes(x= 1962,  y = 3), label = "Seafood", color = 'purple3', fontface = "bold", size = 4)+
  
## Segment : Adding line or we can say connecting comment with linegraph.
geom_segment(aes(x = 1973, y= 80, xend = 1973, yend = 100), size = .5, color = 'red')+
geom_segment(aes(x = 1992, y= 65, xend = 1992, yend = 93), size = .5, color = 'black')+
geom_segment(aes(x = 1982, y= 47, xend = 1982, yend = 28), size = .5, color = 'black')+ 

## geom_point ( Till 2017 as 2018 is being continued)
geom_point(aes(x= 2017, y = 56.5), size = 3, color = "red4")+ # Adding final dot at the end representing till 2017 analysis for Beef
geom_point(aes(x = 2017, y = 56.5), size = 4, color = "grey", alpha = 0.4)+
geom_point(aes(x= 2017, y = 92), size = 3, color = "green4")+ # Adding final dot at the end for Chicken
geom_point(aes(x = 2017, y = 92), size = 4, color = "grey", alpha = 0.4)+
geom_point(aes(x= 2017, y = 92), size = 3, color = "yellow4")+ # Adding final dot at the end for Broilers
geom_point(aes(x = 2017, y = 92), size = 4, color = "grey", alpha = 0.4)+
geom_point(aes(x= 2017, y = 50.5), size = 3, color = "blue")+ # Adding final dot at the end for Pork
geom_point(aes(x = 2017, y = 50.5), size = 4, color = "grey", alpha = 0.4)+
geom_point(aes(x= 2016, y = 14), size = 3, color = "pink")+ # Adding final dot at the end for turkey 
geom_point(aes(x= 2017, y = 16), size = 3, color = "purple")+ # Adding final dot at the end for seafood

  
# Adding continous scale
scale_y_continuous(breaks = c(0,15,30, 45, 60, 75, 90, 105, 120))+
scale_x_continuous(breaks = c(1960, 1970, 1980, 1990, 2000, 2010, 2020))+

# Adjusting uniform parameters
geom_hline(yintercept = 0, size = 1)+ # Adds a black solid line on X-axis and starts from 0
scale_color_manual(values = c("red","green4","yellow","blue", "pink", "purple")) + # Switch around and the color of meat changes according to position.
  


# Title
labs(title = "Chicken consumption has outsupplied Beef and Pork and continues to grow", # Main Tittle
     subtitle = "From year 1986 Consumption of beef has declined tremendously", # sub- title
     caption = "Source: National Chicken Council | Source:USDA", # look at bottom
     x = 'Years', y = "Consumed meats in Pounds") + # X -label & Y-label
  
# Theme
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
theme(legend.position = "none",
          plot.title = element_text(size = 12, face = "bold"), # makes heading bold
          plot.subtitle = element_text(size = 10), # makes subheading bold
      
          axis.title.x = element_text(size = 10, face = "bold"), # word Year
          axis.title.y = element_text(size = 10, face = "bold"), # word consumed meats in pound
        
          axis.text.x = element_text(size = 8, face = "bold"), # X-axis label year 
          axis.text.y = element_text(size = 8)) # Y-axis label 0-100

# Lets save the graph
ggsave("chkn_vs_beef_pork.png", g_sales, width = 12, height = 18, units = "in")
  ###
  
g_sales
```
# Analysis:

1. Year 1973 : Beef Shortage
2. Chicken and Broilers growth continues. They both go hand in hand. No any strange pattern.
3. The First Global Energy Crisis of 1973-1974 where consumption of beef took a hit.
4. We can see drop in pork market share as well but chicken consumption thrive to grow.
5. Seafood and Turkey consumption didn't get affected but in recent years it is still consuming the market.
```{r}
```
# Lets plot another graph based on seafood and Turkey comparison.
```{r}
head(poultry_df, 3)
```
# Lets focus on this time seafood and turkey
```{r}
seafood_turkey_data<- poultry_df %>% 
              select(-c(11:13)) %>% 
              gather("type_of_meat", "poultry_df", 6:7)
head(seafood_turkey_data)

# Data
g_seafood_turkey <- ggplot()+
  geom_line(data = seafood_turkey_data, aes ( x= Year, y = poultry_df, group = factor(type_of_meat), color = factor(type_of_meat)), size = 2, alpha = 1.0)+
  
# Adding geom_point [Intersection]
geom_point(aes(x= 1987.8, y = 15.3), size = 4, color = 'grey')+ # The value x= 1973 and y= 81 is from looking at graph and adding big red dot(POINT)
  
# Lets add some text in graph
geom_text(aes (x = 1985, y = 20), label = "Turkey surpass Seafood consumption: 1987", hjust = 0, color = 'red', fontface = "bold")+
  
# Lets label 
geom_text(aes(x= 1962,  y = 5), label = "Turkey", color = 'pink3', fontface = "bold", size = 4)+ # Turkey
geom_text(aes(x= 1962,  y = 9), label = "Seafood", color = 'purple3', fontface = "bold", size = 4)+ # Seafood

## Segment : Adding line or we can say connecting comment with linegraph.
geom_segment(aes(x = 1988, y= 15.5, xend = 1988, yend = 19.5), size = .5, color = 'black')+
  
## geom_point [Till year 2017]
geom_point(aes(x= 2017, y = 16.5), size = 2.0, color = "black")+ # Adding final dot at the end
geom_point(aes(x = 2016.1, y = 14.5), size = 2.0, color = "black")+
  
# Adding continous scale
scale_y_continuous(breaks = c(0,2,4,6,8,10,12,14,16,18,20))+
scale_x_continuous(breaks = c(1960, 1970, 1980, 1990, 2000, 2010, 2020))+

# Adjusting uniform parameters
geom_hline(yintercept = 0, size = 1)+ # Adds a black solid line on X-axis and starts from 0
scale_color_manual(values = c( "purple", "pink")) + # Switch around and the color of meat changes according to position.

# Title
labs(title = "Seafood and Turkey are uneffected by Chicken consumption growth", # Main Tittle
     subtitle = "Turkey and Seafood are doing equal in a market", # sub- title
     caption = "Source: National Chicken Council | Source:USDA", # look at bottom
     x = 'Years', y = "Consumed meats in Pounds") + # X -label & Y-label
  
# Theme
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+ 
theme(legend.position = "none",
          plot.title = element_text(size = 14, face = "bold"), # makes heading bold
          plot.subtitle = element_text(size = 12), # makes subheading bold
      
          axis.title.x = element_text(size = 10, face = "bold"), # word Year
          axis.title.y = element_text(size = 10, face = "bold"), # word consumed meats in pound
        
          axis.text.x = element_text(size = 8, face = "bold"), # X-axis label year 
          axis.text.y = element_text(size = 8)) # Y-axis label 0-100

# Lets save the graph
ggsave("turkey_vs_seafood.png", g_sales, width = 12, height = 18, units = "in")

g_seafood_turkey

```
# Analysis of Turkey and Seafood

* we don't have future data for Seafood. Data until 2016
* Seems like most of people in USA doesnt consume seafood or Turkey
* Turkey might be consumed more on thanksgiving day 
* Seafood might be consumed only in Coast line. East-coast or west coastline. 
* Nothing so much in middle of country as It's not so fresh as well as price do play a factor
```{r}
```
# PRICE Analysis

# Wholesale and Retail Prices for Chicken (Broilers), Beef ,Pork
** We don't have a price for seafood or turkey to compare
this can be extracted from the same website 
```{r}
url2 <- "https://www.nationalchickencouncil.org/about-the-industry/statistics/wholesale-and-retail-prices-for-chicken-beef-and-pork/"

price_list <- read_html(url2) %>% 
              html_table()
```
NOTE Wholesale beef price is wholesale choice grade value adjusted to wholesale weight equivalent using a coefficient of 1.142 (1.1428 for 2000 on). Wholesale pork price is wholesale value adjusted to wholesale weight equivalent using coefficient of 1.06 (1.04 for 2000 on). Retail prices for choice beef and pork are weighted composite prices as used by USDA in their farm to retail price spread series. Wholesale and retail broiler price are composite prices of parts from 1990 forward. USDA’s New York wholesale whole-carcass broiler price from 1960 to 1963; from 1964 to May 1983 USDA’s 9 city composite wholesale broiler price used from June 1983 to 1989 USDA’s 12-city wholesale, whole-carcass composite price used.
```{r}
price_df <- data.frame(price_list[[1]]) # we dont need to provide [[1]] as there is only one list but we have more than that then we need to specify.
head(price_df)
dim(price_df) # 49 Rows 7 column
colnames(price_df)
```
# Lets look at stat
```{r}
skim(price_df)
```
# Let's fix some columns by renaming it
First two rows are just header so we can slice data from 3rd row.
```{r}
price_df <- price_df %>% 
          slice(3:49) %>% 
          rename(Year = Var.1, 
                 Beef_wholesale_price = WHOLESALE.PRICE, 
                 Pork_wholesale_price = WHOLESALE.PRICE.1, 
                 Chicken_wholesale_price = WHOLESALE.PRICE.2,
                 Beef_retail_price = RETAIL.PRICE,
                 Pork_retail_price = RETAIL.PRICE.1,
                 Chicken_retail_price = RETAIL.PRICE.2
                 )
head(price_df, 3)
```
# Lets fix the year column
```{r}
price_df$Year <- gsub("[^0-9]","",price_df$Year)
tail(price_df)
class(price_df$Year)
```
# Lets fix the year column 
```{r}
price_df$Year <- as.numeric(price_df$Year)
class(price_df$Year)
```

# Modify_at
```{r}
price_df <- price_df%>% 
            select(Year,Beef_retail_price, Pork_retail_price, Chicken_retail_price) %>%  # retail_price
            modify_at(c(1,2,3,4), as.numeric) %>% # Modify at need to know and explain
            gather("type_of_meat", "price", 2:4) %>% 
            mutate(price_dollar = price/100) # cents per lb. on a wholesale weight so we have now $ price
head(price_df)
```
# plot for sales of each meat over time
* type_of_meat is character so we have to factor before we plot.
* size : width of line
* alpha : Transperancy of line
```{r}
tail(price_df)
```

```{r}
g_price <- ggplot()+
  geom_line(data = price_df, aes(x = Year, y= price_dollar, group = factor(type_of_meat), color = factor(type_of_meat)), size =2, alpha = 0.7)+
  
# Adding geom_point at the end
geom_point(aes(x = 2017, y = 5.92), size = 3, color = "red") +
geom_point(aes(x = 2017, y = 3.78), size = 3, color = "blue") +
geom_point(aes(x = 2017, y = 1.90), size = 3, color = "green4")+
  
#geom_text
geom_text(aes(x = 2011, y = 6.5), label = "Beef - $5.85", color = "red", fontface = "bold", size = 4) +
geom_text(aes(x = 2011, y = 2.5), label = "Pork - $3.78", color = "blue", fontface = "bold", size = 4) +
geom_text(aes(x = 2011, y = 1.1), label = "Chicken - $1.96", color = "green4", fontface = "bold", size = 4) +
# Lets add some text in graph
geom_text(aes (x = 1995, y = 5), label = "2000 :Beef @ 3.00", hjust = 0, color = 'red', fontface = "bold")+
  
## Segment : Adding line or we can say connecting comment with linegraph.
geom_segment(aes(x = 2000, y= 4.9, xend = 2000, yend = 3.2), size = .5, color = 'black')+
  
# Title  
labs(title = "Price of chicken is rising compare to falling price of Pork and Beef ",
subtitle = "Price of beef is falling down because of less consumption",
caption = "Source: National Chicken Council                                           Source : USDA",
x = "Years", y = "PRICE PER POUND ($)") +
  
# Setting up parameters  
scale_y_continuous(breaks = seq(0, 6, 1)) +
scale_x_continuous(breaks = seq(1960, 2020, 5)) + 
geom_hline(yintercept = 0, size = 1) +
xlab("") +
ylab("Dollar per lb of meat") +
scale_color_manual(values = c("red", "green4", "blue")) +
  
# Theme  
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
theme(legend.position = "none",
          plot.title = element_text(size = 14, face = "bold"),
          plot.subtitle = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10))
          
g_price
```
# Analysis
* We don't have price for Seafood and Turkey.
* price of Beef has almost doubled in past 20 years
* Consumption of beef is falling down from 2015.
* From 2000 beef has been consumed more than chicken
```{r}
percent_poultry_df <- poultry_df %>% 
                    select(Year, 8:13) %>%  # We will select Year, and percentage change in poultry products
                    rename(Beef_p = percent_change_Beef, 
                           Pork_p = percent_change_Pork,
                           broilers_p = percent_change_Broilers,
                           Chicken_p = percent_change_Chicken,
                           Turkey_p = percent_change_Turkey,
                           Seafood_p = percent_change_Seafood ) %>%  # Lets create a simple name so that its clear and crisp. and also we are just selecting column 6 to 10 that is with percentage.
                          gather("type_of_meat", "change_in_percent", 2:7)
head(percent_poultry_df, 10) # See it gather according type of meat.
tail(percent_poultry_df, 10) # See it gather according type of meat.
```
# Percent consumption change Graph
```{r}
g_pcnt <- ggplot()+
  geom_line(data = percent_poultry_df, aes(x = Year, y = change_in_percent, group = factor(type_of_meat), color = factor(type_of_meat)), size = .5)+

# Lets label Chicken, pork ,beef, Turkey, broilers and Beef POSITION
geom_text(aes(x= 2018,  y = 6), label = "Beef", color = 'red3', fontface = "bold", size = 4)+
geom_text(aes(x= 2018,  y = 300), label = "Chicken", color = 'green3', fontface = "bold", size = 4)+
geom_text(aes(x= 2018,  y = 250), label = "Broilers", color = 'yellow3', fontface = "bold", size = 4)+
geom_text(aes(x= 2018,  y = -25), label = "Pork", color = 'blue3', fontface = "bold", size = 4)+
geom_text(aes(x= 2018,  y = 60), label = "Turkey", color = 'pink3', fontface = "bold", size = 4)+
geom_text(aes(x= 2018,  y = 180), label = "Seafood", color = 'purple3', fontface = "bold", size = 4)+

scale_y_continuous(breaks = seq(0, 300, 50)) +
scale_x_continuous(breaks = seq(1960, 2020, 5)) + 

# Adjusting uniform parameters
scale_color_manual(values = c("red","green4","yellow","blue", "pink", "purple")) + # Switch around and the color of meat changes according to position.
geom_hline(yintercept = 0, size = 1, color = "black", alpha = 0.5) +  # Adds a black solid line on X-axis and starts from 0
xlab("") +
ylab("Percent") +
  
# Title
labs(title = "Change in percentage consumption of poultry products over course of year", # Main Tittle
     caption = "Source: National Chicken Council | Source:USDA", # look at bottom
     x = 'Years', y = "Consumed meats in Pounds") + # X -label & Y-label
  
# Theme  
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
theme(legend.position = "none",
          plot.title = element_text(size = 12, face = "bold"), # makes heading bold
         
          axis.title.x = element_text(size = 10, face = "bold"), # word Year
          axis.title.y = element_text(size = 10, face = "bold"), # word consumed meats in pound
        
          axis.text.x = element_text(size = 8, face = "bold"), # X-axis label year 
          axis.text.y = element_text(size = 8)) # Y-axis label 0-100

# Lets save the graph
ggsave("pcnt_consumption.png", g_sales, width = 12, height = 18, units = "in")
g_pcnt
```
# Analysis

1. price of pork hasn't risen and overall its is declining
2. Price of beef has fallen down
3. Chicken has been consumed almost 300 %  from year 1960.
4. Beef and pork are less favorable food of consumption.
5. We can see huge spike in seafood in year 1985 to 1990 then it flats out.
6. We can see the difference in what called broilers consumption and chicken consumption.
```{r}
```
I hope you guys find this plot helpful in understanding so that you can plot your own graph yourself. This plot is modification on someone else work not a orginal creation but inspiration to create a plot like that in my own version.
```{r}
#render("chicken.Rmd", html_document(df_print = pander))
```

